Why there are more species in several small patches vs few large patches:

### 2024-03-19 ms_SLOSS.Rmd
Minor Changes to submit

---
title: "Why there are more species in several small patches vs few large patches:
  a multi-species modeling approach"
bibliography: sloss_bib.bib
csl: "ecology-letters.csl"

>>>>

---
title: "Why there are more species in several small patches vs few large patches:
  a multi-species modeling approach"
bibliography: sloss_bib.bib
csl: "functional-ecology.csl"
